### 2013-01-15 Docs/managing_jobs/managingjobs.tex
add note about MPI error on hopper

hopper is configured with 24 cores per node, with the cores grouped
into 4 NUMA nodes of 6 cores each.  Best performance is seen when
running with 6 threads and 4 MPI tasks per node, using the following
run line:
\begin{verbatim}
aprun -n 128 -N 4 -d 6 -S 1 -ss ./main.Linux.Cray.mpi.omp.ex inputs_3d
\end{verbatim}
Here, {\tt -n} is the number of MPI tasks, and {\tt n * d} is the
total number of cores (which should match the {\tt mppwidth} set at
the top of the submission script).

>>>>

hopper is configured with 24 cores per node, with the cores grouped
into 4 NUMA nodes of 6 cores each.  Best performance is seen when
running with 6 threads and 4 MPI tasks per node, using the following
run line:
\begin{verbatim}
aprun -n 128 -N 4 -d 6 -S 1 -ss ./main.Linux.Cray.mpi.omp.ex inputs_3d
\end{verbatim}
Here, {\tt -n} is the number of MPI tasks, and {\tt n * d} is the
total number of cores (which should match the {\tt mppwidth} set at
the top of the submission script). \\

\noindent (2013-01-15) It's been seen that sometimes an MPICH2 error is 
generated of the form:
\begin{verbatim}
MPIU_nem_gni_get_hugepages(): Unable to mmap 8388608 bytes for file 
/var/lib/hugetlbfs/global/pagesize-2097152/hugepagefile.MPICH.1.19467.kvs_14619732, 
err Cannot allocate memory
\end{verbatim}
Setting:
\begin{verbatim}
export MPICH_GNI_MALLOC_FALLBACK=enabled
\end{verbatim}
in your submission script seems to fix this issue.  This will allow
MPI to continue if there are insufficient huge pages in one NUMA node.
(Alternately, it was suggested to run without the {\tt -ss} option to
{\tt aprun}.
